Variation in site entropy explains differences in structure-sequence relationships of proteins

### 2015-06-02 manuscript/manuscript.tex
Making changes to figures

            \begin{figure}[H]
            \centerline{\includegraphics[width=5.0in]{var_rate_rsa_cor.pdf}}     
            \caption{Comparison of the correlations between RSA and Rate4Site and the variance of Rate4Site at sites. The enzyme proteins are colored in black and the virus proteins are visualized in red. The variance of evolutionary rate of a protein, as measured by Rate4Site, does not have a correlation with the spearman correlation between RSA and evolutionary rate for a given protein.}
            \label{fig:var_rate_rsa_cor}
    \end{figure}

@@

        \begin{figure}[H]
            \centerline{\includegraphics[width=7.5in]{protein_ex_plot.pdf}}     
            \caption{Comparison of the mean entropy and the variance of entropy for individual proteins. A)  Variance in entropy at sites compared against overall mean entropy for proteins. Four proteins of interest are highlighted by open circles. The enzyme proteins are colored in black and the virus proteins are colored red B) Distributions of site-wise entropy values for the four enzyme proteins highlighted in A. There are a variety of distributions in site entropy for different proteins.}
            \label{fig:protein_ex_plot}
    \end{figure}

\begin{center}
	\begin{table}[H]
	\begin{tabular}{| p{1.5cm} | p{2.5cm} | p{2cm} | p{2cm} | }
		\hline
		Dataset & Mean $\rho$ Entropy-CN  & Mean $\rho$ Entropy-WCN & Mean $\rho$ Entropy-RSA \\
		\hline	
		Enzyme &  $-0.445$  & $-0.432$ & $0.464$ \\
		\hline
		Virus & $-0.213$ & $-0.217$ & $0.237$ \\
		\hline	
	\end{tabular}
	\caption{Averages of the Spearman Correlation Coefficients between Structural Properties and Entropy. The structural properties analyzed are solvent accessibility as calculated by RSA and packing density as calculated by CN and WCN.}
	\label{table:entropy_stats}
	\end{table}
\end{center}

\begin{center}
	\begin{table}[H]
	\begin{tabular}{| p{1.5cm} | p{2.5cm} | p{2cm} | p{2cm} |  }
		\hline
		Dataset & Mean $\rho$ Rate4Site-CN  & Mean $\rho$ Rate4Site-WCN & Mean $\rho$ Rate4Site-RSA \\
		\hline	
		Enzyme &  $-0.445$  & $-0.432$ & $0.464$ \\
		\hline
		Virus & $-0.213$ & $-0.217$ & $0.237$ \\
		\hline	
	\end{tabular}
	\caption{Averages of the Spearman Correlation Coefficients between Structural Properties and Evolutionary Rate. Evolutionary rate is calculated with Rate4Site. The structural properties analyzed are solvent accessibility as calculated by RSA and packing density as calculated by CN and WCN.}
	\label{table:rate_stats}
	\end{table}
\end{center}

%Should I report the intercept%
\begin{center}
	\begin{table}[H]
	\begin{tabular}{ | p{5.0cm} | p{3cm} | p{3cm} | p{3cm} | }
	\hline
	Model & Coefficient x  & Coefficient y & Coefficient z \\	
	\hline
	CN-Entropy $\rho$ $ = $ Mean Entropy + Dataset + Dataset*Mean Entropy & $0.079 ^{**}$ & $0.382^{***}$  & $-0.583$ \\	
	\hline
	WCN-Entropy $\rho$ $ = $ Mean Entropy + Dataset + Dataset*Mean Entropy & $0.049$ & $0.323^{***}$ & $-0.568$  \\	
	\hline

	RSA-Entropy $\rho$ $ = $ Mean Entropy + Dataset + Dataset*Mean Entropy &  $-0.0300$ & $-0.336^{***}$ & $0.903^{*}$ \\

	\hline
	CN-Entropy $\rho$ $ = $ Variance Entropy + Dataset + Dataset*Variance Entropy & $-0.522^{***}$ &  $0.013$ & $-0.265$ \\	
	\hline
	WCN-Entropy $\rho$ $ = $ Variance Entropy + Dataset + Dataset*Variance Entropy & $-0.464^{***}$ &  $0.023$ & $-0.325$ \\	
	\hline
	RSA-Entropy $\rho$ $ = $ Variance Entropy + Dataset + Dataset*Variance Entropy & $0.415^{***}$ & $-0.076$ & $0.927$ \\

>>>>

            \begin{figure}[H]
            \centerline{\includegraphics[width=4in]{var_rate_rsa_cor.pdf}}     
            \caption{Comparison of the correlations between RSA and Rate4Site and the variance of Rate4Site at sites. The enzyme proteins are colored in black and the virus proteins are visualized in red. The variance of evolutionary rate of a protein, as measured by Rate4Site, does not have a correlation with the spearman correlation between RSA and evolutionary rate for a given protein.}
            \label{fig:var_rate_rsa_cor}
    \end{figure}

@@

        \begin{figure}[H]
            \centerline{\includegraphics[width=7.5in]{protein_ex_plot.pdf}}     
            \caption{Comparison of the mean entropy and the variance of entropy for individual proteins. A)  Variance in entropy at sites compared against overall mean entropy for proteins. Four proteins of interest are highlighted by open circles. The enzyme proteins are colored in black and the virus proteins are colored red B-F) Distributions of site-wise entropy values for the five enzyme proteins highlighted in A. There are a variety of distributions in site entropy for different proteins.}
            \label{fig:protein_ex_plot}
    \end{figure}

\begin{center}
	\begin{table}[H]
	\begin{tabular}{| p{1.5cm} | p{2.5cm} | p{2cm} | p{2cm} | }
		\hline
		Dataset & Mean $\rho$ Entropy-CN  & Mean $\rho$ Entropy-WCN & Mean $\rho$ Entropy-RSA \\
		\hline	
		Enzyme &  $-0.445$  & $-0.432$ & $0.464$ \\[0.10cm]

		Virus & $-0.213$ & $-0.217$ & $0.237$ \\
		\hline	
	\end{tabular}
	\caption{Averages of the Spearman Correlation Coefficients between Structural Properties and Entropy. The structural properties analyzed are solvent accessibility as calculated by RSA and packing density as calculated by CN and WCN.}
	\label{table:entropy_stats}
	\end{table}
\end{center}

\begin{center}
	\begin{table}[H]
	\begin{tabular}{| p{1.5cm} | p{2.5cm} | p{2cm} | p{2cm} |  }
		\hline
		Dataset & Mean $\rho$ Rate4Site-CN  & Mean $\rho$ Rate4Site-WCN & Mean $\rho$ Rate4Site-RSA \\
		\hline	
		Enzyme &  $-0.445$  & $-0.432$ & $0.464$ \\[0.10cm]

		Virus & $-0.213$ & $-0.217$ & $0.237$ \\
		\hline	
	\end{tabular}
	\caption{Averages of the Spearman Correlation Coefficients between Structural Properties and Evolutionary Rate. Evolutionary rate is calculated with Rate4Site. The structural properties analyzed are solvent accessibility as calculated by RSA and packing density as calculated by CN and WCN.}
	\label{table:rate_stats}
	\end{table}
\end{center}

%Should I report the intercept%
\begin{center}
	\begin{table}[H]
	\begin{tabular}{ | p{5.0cm} | p{3cm} | p{3cm} | p{4cm} | }
	\hline
	Model & $\left \langle H \right \rangle$  & Dataset & Dataset*$\left \langle H \right \rangle$ \\	
	\hline
	$\rho  \text{\_CN--H}$   $ = $  $\left \langle H \right \rangle$ + Dataset + Dataset*$\left \langle H \right \rangle$ & $0.079 ^{**}$ & $0.382^{***}$  & $-0.583$   \\[1.2cm]

	$\rho  \text{\_WCN--H}$  $ = $  $\left \langle H \right \rangle$ + Dataset + Dataset*$\left \langle H \right \rangle$& $0.049$ & $0.323^{***}$ & $-0.568$  \\[1.2cm]

	$\rho  \text{\_RSA--H}$  $ = $ $\left \langle H \right \rangle$ + Dataset + Dataset*$\left \langle H \right \rangle$ &  $-0.030$ & $-0.336^{***}$ & $0.903^{*}$ \\[1.2cm]

	$\rho  \text{\_CN--H}$   $ = $  $\left \langle H \right \rangle$ + Dataset + Dataset*$\left \langle H \right \rangle$ & $0.077^{**}$ & $0.336^{***}$  & NA  \\[1.2cm]

	$\rho  \text{\_WCN--H}$  $ = $  $\left \langle H \right \rangle$ + Dataset + Dataset*$\left \langle H \right \rangle$& $ 0.047$ & $0.278^{***}$ & NA  \\[1.2cm]

	$\rho  \text{\_RSA--H}$  $ = $ $\left \langle H \right \rangle$ + Dataset + Dataset*$\left \langle H \right \rangle$ &  $-0.027$ & $ -0.264^{***}$ & NA \\

\begin{center}
	\begin{table}[H]
	\begin{tabular}{ | p{5.0cm} | p{3cm} | p{3cm} | p{4cm} | }
	\hline
	Model & Variance H  & Dataset & Dataset*Variance H \\	
	\hline
	$\rho  \text{\_CN--H}$ $ = $ Variance H + Dataset + Dataset*Variance H & $-0.522^{***}$ &  $0.013$ & $-0.265$ \\[1.3cm]

	$\rho  \text{\_WCN--H}$ $ = $ Variance H + Dataset + Dataset*Variance H& $-0.464^{***}$ &  $0.023$ & $-0.325$ \\ [1.3cm]

	$\rho  \text{\_RSA--H}$ $ = $ Variance H + Dataset + Dataset*Variance H & $0.415^{***}$ & $-0.076$ & $0.927$ \\

		$\rho  \text{\_CN--H}$ $ = $ Variance H + Dataset + Dataset*Variance H & $-0.524^{***}$ &  $0.004$ & NA \\[1.3cm]

	$\rho  \text{\_WCN--H}$ $ = $ Variance H + Dataset + Dataset*Variance H& $-0.466 ^{***}$ &  $ 0.012$ & NA \\ [1.3cm]

	$\rho  \text{\_RSA--H}$ $ = $ Variance H + Dataset + Dataset*Variance H & $0.422^{***}$ & $-0.044$ & NA \\
